### 2017-01-08 MSSM/MSSM.tex
Adding more MSSM text

\begin{figure}[h!]
\begin{center}
\subfloat[$m_{\phi} = 160$ GeV]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/optimisation_ggh_mt_160.0_range12.pdf}}
\subfloat[$m_{\phi} = 900$ GeV]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/optimisation_ggh_mt_900.0_range12.pdf}}~\\
\subfloat[$m_{\phi} = 1600$ GeV]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/optimisation_ggh_mt_1600.0_range12.pdf}}
\subfloat[$m_{\phi} = 2900$ GeV]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/optimisation_ggh_mt_2900.0_range12.pdf}}
\end{center}
\caption{Pre--fit expected limit on $\sigma\times$BR for the gg$\phi$ production process with decay into $\Pgt\Pgt$,
s a function of tau isolation working point (from very loose to very very tight) and
of \mT~ cut from \mT$<20$ GeV to \mt$<40$ GeV, normalised to the best limit in the plane, indicated by the asterisk. This is shown
for $m_{\phi}$ = 160 GeV (a), 900 GeV (b), 1600 GeV (c) and 2900 GeV (d). The most optimal combination of \mT~selection and 
hadronic tau isolation working point varies by mass point, with looser selections preferred for higher masses.}
\label{fig:mssm_selection_mt_taumt}.
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\subfloat[gg$\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_optimisation_mediummt40_vs_tightmt30pt20_mt_ggH.png}}
\subfloat[bb$\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_optimisation_mediummt40_vs_tightmt30pt20_mt_bbH.png}}
\end{center}
\caption{Pre-fit expected limits on $\sigma\times$BR in the \mutau channelfor (a) gg$\phi$ production and (b) bb$\phi$ production. The
limits using the medium hadronic tau isolation working point and \mT$<40$ GeV selection using a minimum
hadronic tau \pT~cut of 20 GeV (black circles), 30 GeV (blue circles) and 40 GeV (red circles). The green
circles show the limits using tighter tau isolation working point and \mT~selection. The limits on
the gg$\phi$ production process improve at low masses when increasing the hadronic tau \pT~cut,
the effect on the bb$\phi$ production process is less pronounced. FIXME REMAKE PLOT}
\label{fig:mssm_tauptcut}
\end{figure}

@@

Just like for muons, it was found that the analysis is not highly sensitive
to the choice of electron isolation variable and selection, yet an effort
is made not to use a suboptimal selection.
A topological selection on the \mT~ variable is also made in this channel to reject \Wjets events. 
The used value of $\mT < 50$ is obtained by performing a 2D optimisation where the \mT~ selection
and hadronic tau isolation working point are varied at the same time. The same considerations as
for the \mutau channel apply. The choice of the hadronic tau \pT~ selection to 30 GeV is
chosen to recover some of the sensitivity lost at low mass by using looser \mT~ and hadronic
tau isolation selections. This is illustrated in figure \ref{fig:mssm_tauptcut_et}.

\begin{figure}[h!]
\begin{center}
\subfloat[gg$\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_optimisation_mediummt50_vs_tightmt40pt20_et_ggH.png}}
\subfloat[bb$\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_optimisation_mediummt50_vs_tightmt40pt20_et_bbH.png}}
\end{center}
\caption{Pre-fit expected limits on $\sigma\times$BR in the \etau channel for (a) gg$\phi$ production and (b) bb$\phi$ production. The
limits using the medium hadronic tau isolation working point and \mT$<40$ GeV selection using a minimum
hadronic tau \pT~cut of 20 GeV (black circles), 30 GeV (blue circles) and 40 GeV (red circles). The green
circles show the limits using tighter tau isolation working point and \mT~selection. The limits on
the gg$\phi$ production process improve at low masses when increasing the hadronic tau \pT~cut,
the effect on the bb$\phi$ production process is less pronounced. FIXME REMAKE PLOT}
\label{fig:mssm_tauptcut_et}
\end{figure}

@@

Thus $D_{\zeta}$ is the difference of the projection of the visible tau decay products plus missing energy \pT+\MET,
and simply the visible tau decay product \pT on the axis $\vec{\zeta}$. This is the axis that bisects 
the directions $\vec{p}_{\text{T,1}}^{\text{vis}}$ and $\vec{p}_{\text{T,2}}^{\text{vis}}$
of the visible decay products in the transverse plane. This selection is illustrated in figure
\ref{fig:mssm_dzeta}a, with figure \ref{fig:mssm_dzeta}b showing the $D_{\zeta}$ distribution
for \emu events. The used cut value, $D_{\zeta} > -20$ GeV rejects $\ttbar$, \Wjets and diboson
events.

\begin{figure}[h!]
\begin{center}
\subfloat[Reconstruction of $D_{\zeta}$]{./includegraphics[width=0.5\textwidth]{./MSSM/Figures/PZeta.pdf}}
\subfloat[$D_{\zeta}$ distribution in \emu channel]{./includegraphics[width=0.5\textwidth]{./MSSM/Figures/pzeta_inclusive_em_2016.pdf}}
\end{center}
\caption{(a) reconstruction of $D_{\zeta}$ \cite{cdf-dzeta} and (b) $D_{\zeta}$ distribution in the 
\emu channel\cite{CMS-PAS-HIG-16-037}.}
\label{fig:mssm_dzeta}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\subfloat[Number of jets]{/includegraphics[width=0.5\textwidth]{./MSSM/Figures/n_jets_inclusive_tt_2016_log.png}}
\subfloat[Number of b--tagged jets]{/includegraphics[width=0.5\textwidth]{./MSSM/Figures/n_bjets_inclusive_tt_2016_log.png}}
\end{center}
\caption{(a) Number of jets and (b) number of b--tagged jets in the \tautau channel. The gluon--gluon fusion signal (COLOUR)
and bb--associated signal (COLOUR2) are overlaid on the distribution, motivating the choice of
categorisation to target the two different signals. FIXME REMAKE THESE PLOTS WITH SIGNAL ON!
\label{fig:mssm_cats_tt}
\end{figure}

\section{\ac{MC} to data correction factors}
\label{sec:mssm_mccorrs}

@@

\section{Background estimation}
\label{sec:mssm_bkgs}
The methods used for background estimation will be described in this
channel. The background estimation in the \etau and \mutau channels
is very similar and they are combined

\subsection{\texorpdfstring{\mutau and \etau channels}{mutau and etau channels}}
\label{sec:mssm_bkgs_mtet}

\subsubsection{\texorpdfstring{\Ztautau}{Z to tau tau}}
\label{sec:mssm_bkgs_mtet_ztt}

\subsubsection{\texorpdfstring{\Wjets}{W+jets}}
\label{sec:mssm_bkgs_mtet_wjets}

\subsubsection{QCD}
\label{sec:mssm_bkgs_mtet_qcd}

\subsubsection{\texorpdfstring{\ttbar}{ttbar}}
\label{sec:mssm_bkgs_mtet_tt}

\subsubsection{Other backgrounds}
\label{sec:mssm_bkgs_mtet_other}

\subsection{\texorpdfstring{\tautau channel}{tautau channel}}
\label{sec:mssm_bkgs_tt}

\subsubsection{\texorpdfstring{\Ztautau}{Z to tau tau}}
\label{sec:mssm_bkgs_tt_ztt}

\subsubsection{QCD}
\label{sec:mssm_bkgs_tt_qcd}

\subsubsection{\texorpdfstring{\Wjets}{W+jets}}
\label{sec:mssm_bkgs_tt_wjets}

\subsubsection{\texorpdfstring{\ttbar}{ttbar}}
\label{sec:mssm_bkgs_tt_tt}

\subsubsection{Other backgrounds}
\label{sec:mssm_bkgs_tt_other}

\subsection{\texorpdfstring{\emu channel}{emu channel}}
\label{sec:mssm_bkgs_em}

\subsubsection{\texorpdfstring{\Ztautau}{Z to tau tau}}
\label{sec:mssm_bkgs_em_ztt}

\subsubsection{QCD}
\label{sec:mssm_bkgs_em_qcd}

\subsubsection{\texorpdfstring{\Wjets}{W+jets}}
\label{sec:mssm_bkgs_em_wjets}

\subsubsection{\texorpdfstring{\ttbar}{ttbar}}
\label{sec:mssm_bkgs_em_tt}

\subsubsection{Other backgrounds}
\label{sec:mssm_bkgs_em_other}

\section{Systematic uncertainties}
\label{sec:mssm_uncs}

\subsection{Normalisation uncertainties}
\label{sec:mssm_uncs_norm}

\subsection{Shape uncertainties}
\label{sec:mssm_uncs_shape}

>>>>

\begin{figure}[h!]
\begin{center}
\subfloat[$m_{\phi} = 160$ GeV]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/optimisation_ggh_mt_160_range12.pdf}}
\subfloat[$m_{\phi} = 900$ GeV]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/optimisation_ggh_mt_900_range12.pdf}}~\\
\subfloat[$m_{\phi} = 1600$ GeV]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/optimisation_ggh_mt_1600_range12.pdf}}
\subfloat[$m_{\phi} = 2900$ GeV]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/optimisation_ggh_mt_2900_range12.pdf}}
\end{center}
\caption{Pre--fit expected limit on $\sigma\times$BR for the gg$\phi$ production process with decay into $\Pgt\Pgt$,
s a function of tau isolation working point (from very loose to very very tight) and
of \mT~ cut from \mT$<20$ GeV to \mT$<40$ GeV, normalised to the best limit in the plane, indicated by the asterisk. This is shown
for $m_{\phi}$ = 160 GeV (a), 900 GeV (b), 1600 GeV (c) and 2900 GeV (d). The most optimal combination of \mT~selection and 
hadronic tau isolation working point varies by mass point, with looser selections preferred for higher masses.}
\label{fig:mssm_selection_mt_taumt}.
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\subfloat[gg$\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_optimisation_mediummt40_vs_tightmt30pt20_mt_ggH_remake.pdf}}
\subfloat[bb$\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_optimisation_mediummt40_vs_tightmt30pt20_mt_bbH_remake.pdf}}
\end{center}
\caption{Pre-fit expected limits on $\sigma\times$BR in the \mutau channel for (a) gg$\phi$ production and (b) bb$\phi$ production. The
limits when using the medium hadronic tau isolation working point and \mT$<40$ GeV selection using a minimum
hadronic tau \pT~cut of 20 GeV (red circles), 30 GeV (blue circles) and 40 GeV (black circles) are shown. The green
circles show the limits using tighter tau isolation working point and \mT~selection. The limits on
the gg$\phi$ production process improve at low masses when increasing the hadronic tau \pT~cut,
the effect on the bb$\phi$ production process is less pronounced.}
\label{fig:mssm_tauptcut}
\end{figure}

@@

Just like for muons, it was found that the analysis is not highly sensitive
to the choice of electron isolation variable and selection, yet an effort
is made not to use a suboptimal selection.
A topological selection on the \mT~ variable is also made in this channel to reject \Wjets events. 
The used value of \mT $< 50$ is obtained by performing a 2D optimisation where the \mT~ selection
and hadronic tau isolation working point are varied at the same time. The same considerations as
for the \mutau channel apply. The choice of the hadronic tau \pT~ selection to 30 GeV is
chosen to recover some of the sensitivity lost at low mass by using looser \mT~ and hadronic
tau isolation selections. This is illustrated in figure \ref{fig:mssm_tauptcut_et}.

\begin{figure}[h!]
\begin{center}
\subfloat[gg$\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_optimisation_mediummt50_vs_tightmt40pt20_et_ggH_remake.pdf}}
\subfloat[bb$\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_optimisation_mediummt50_vs_tightmt40pt20_et_bbH_remake.pdf}}
\end{center}
\caption{Pre-fit expected limits on $\sigma\times$BR in the \etau channel for (a) gg$\phi$ production and (b) bb$\phi$ production. The
limits using the medium hadronic tau isolation working point and \mT$<40$ GeV selection using a minimum
hadronic tau \pT~cut of 20 GeV (red circles), 30 GeV (blue circles) and 40 GeV (black circles) are shown. The green
circles show the limits using tighter tau isolation working point and \mT~selection. The limits on
the gg$\phi$ production process improve at low masses when increasing the hadronic tau \pT~cut,
the effect on the bb$\phi$ production process is less pronounced.}
\label{fig:mssm_tauptcut_et}
\end{figure}

@@

Thus $D_{\zeta}$ is the difference of the projection of the visible tau decay products plus missing energy \pT+\MET,
and simply the visible tau decay product \pT on the axis $\vec{\zeta}$. This is the axis that bisects 
the directions $\vec{p}_{\text{T,1}}^{\text{vis}}$ and $\vec{p}_{\text{T,2}}^{\text{vis}}$
of the visible decay products in the transverse plane. This selection is illustrated in figure
\ref{fig:mssm_dzeta}a, with figure \ref{fig:mssm_dzeta}b showing the $D_{\zeta}$ distribution
for \emu events. The used cut value, $D_{\zeta} > -20$ GeV rejects $\ttbar$, \Wjets and diboson
events. 
%The momentum of the neutrinos should not be in the opposite direction of the sum of the visible decay products
%as the neutrinos and visible tau decay products travel at small angles from the original tau.

\begin{figure}[h!]
\begin{center}
\subfloat[Reconstruction of $D_{\zeta}$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/PZeta.pdf}}
\subfloat[$D_{\zeta}$ distribution in \emu channel]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/pzeta_inclusive_em_2016.pdf}}
\end{center}
\caption{(a) reconstruction of $D_{\zeta}$ \cite{cdf-dzeta} and (b) $D_{\zeta}$ distribution in the 
\emu channel\cite{CMS-PAS-HIG-16-037}.}
\label{fig:mssm_dzeta}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\subfloat[Number of jets]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/n_jets_inclusive_tt_2016_log.png}}
\subfloat[Number of b--tagged jets]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/n_bjets_inclusive_tt_2016_log.png}}
\end{center}
\caption{(a) Number of jets and (b) number of b--tagged jets in the \tautau channel. The gluon--gluon fusion signal (COLOUR)
and bb--associated signal (COLOUR2) are overlaid on the distribution, motivating the choice of
categorisation to target the two different signals. FIXME REMAKE THESE PLOTS WITH SIGNAL ON!}
\label{fig:mssm_cats_tt}
\end{figure}

\section{\ac{MC} to data correction factors}
\label{sec:mssm_mccorrs}
\subsubsection*{Tracking efficiency}
\subsubsection*{Electron, muon and tau ID and isolation}
\subsubsection*{Trigger efficiency}
\subsubsection*{$\Pe\rightarrow\Pgt_{h}$ fake rate and $\Pgm\rightarrow\Pgt_{h}$ fake rate}
\subsubsection*{\MET recoil corrections}
\subsubsection*{Top-quark \pT reweighting}
\subsubsection*{Drell-Yan shape reweighting}

@@

\section{Background estimation}
\label{sec:mssm_bkgs}
The methods used for background estimation will be described in this
section. As the \mutau and \etau channels use very similar
background methods, they are described in the same subsection.

\subsection{Generator matching}
\label{sec:mssm_bkgs_genmatch}
For backgrounds estimated from \ac{MC} there are often 
different sub--processes playing a role that should be
treated separately by the fit. Taking the \mutau 
channel as an example, a sample of Drell--Yan events
will contain \Ztautau events, where one of the taus decays
hadronically and the other tau decays to a muon, but also
\Zmm events where one of the muons fakes a tau, or with an 
additional jet in the event faking a hadronic tau and one of the
muons not being properly reconstructed. Similarly, \ttbar background
events can be split into those with genuine taus, and those
where a jet mimics a hadronic tau.

Dividing events from the same production
process into sub--samples
based on generator level information allows
for a more correct treatment of systematic uncertainties.

To determine the generator-level particle
that a reconstructed electron, muon, or hadronic tau
originates from, reconstructed objects are matched
to a set of generator level objects within a cone of $\Delta R = 0.2$.
Five categories of generator-level object are considered for matching:
prompt electrons and muons,
that is electrons and muons not originating from a decay; electrons and muons
from tau decays; and generator-level hadronic taus. These generator-level
hadronic taus are rebuilt by summing the four--momenta
of the visible decay products of the generator-level tau.

All of these particles are looked for in a cone of $\Delta R = 0.2$ around
the reconstructed object, and if there are multiple generator-level
particles within this cone the one nearest the reconstructed particle
is chosen as the object this particle is matched to. If there are no 
generator-level particles in the cone at all it is said to 
have originated from pile--up or a jet at generator level.

The generator--level object type matched to a 
reconstructed particle is used to perform the splitting
of background samples, and is indicated where this is used.

\subsection{\texorpdfstring{\Ztautau}{Z to tau tau}}
\label{sec:mssm_bkgs_ztt}
For all channels, both shape and normalisation of the \Ztautau background 
is estimated from the Drell-Yan
\ac{MC} samples described in section \ref{sec:mssm_datasets}.
For the \mutau and \etau channels, events from these samples 
in which the reconstructed hadronic tau is matched to 
a generator-level hadronic tau are considered part of the \Ztautau
background. In the \tautau channel both reconstructed
hadronic taus are required to be matched to a generator-level hadronic tau, and
in the \emu channel the \Ztautau component of the Drell-Yan background 
is taken as those events where the reconstructed electron is not matched to
a prompt electron at generator level and the reconstructed
muon is not matched to a prompt muon. 
Events in the Drell-Yan samples selected in the event selection
but not satisfying the generator matching requirements are considered
as the, much smaller, \Zll background.

To correct and constrain the \Ztautau normalisation in the
b-tag and no b-tag categories of all channels, \Zmm control
regions are simultaneously fitted. More detail is given in 
section \ref{sec:mssm_sigext_ctrl}.

\subsection{\texorpdfstring{\Wjets and QCD in the \etau and \mutau channels}{W+jets and QCD in the e tau and mu tau channels}}
\label{sec:mssm_bkgs_mtet_wjetsqcd}
A data--driven approach is used for the estimation of
both the \Wjets and QCD backgrounds in the \etau and \mutau channels. 
The estimates of the normalisations of the two backgrounds are tied
together due to the presence of some QCD contamination in the \Wjets--dominated
control region. The shape of the \Wjets background is taken
from the \ac{MC} samples, with the QCD shape taken from same--sign
data with other backgrounds subtracted.

\subsubsection{\texorpdfstring{\Wjets normalisation}{W+jets normalisation}}
\label{sec:mssm_bkgs_mtet_wjetsnorm}
The \Wjets normalisation is derived using a high-\mT~ control region, where
selected events are required to satisfy \mT$>70$ GeV. In the no b-tag
category the \Wjets
contribution in this region is enhanced, however there is still
some contribution from QCD events in this region. Therefore we
have, for \mT$>70$ GeV:

\begin{equation}\label{eqn:wjets_ss_norm}
\begin{split}
N_{\text{data}}^{SS, \text{high } m_{\text{T}}} - N_{\text{other}}^{SS,
\text{high } m_{\text{T}}} & =
N_{\text{QCD}}^{SS, \text{high } m_{\text{T}}} + N_{W}^{SS, \text{high } m_{\text{T}}} ~\\
N_{\text{data}}^{OS, \text{high } m_{\text{T}}} - N_{\text{other}}^{OS,
\text{high } m_{\text{T}}} & = N_{\text{QCD}}^{OS, \text{high } m_{\text{T}}} +
N_{W}^{OS, \text{high } m_{\text{T}}} \\
& = R_{\text{QCD}}^{OS/SS}\cdot N_{\text{QCD}}^{SS, \text{high } m_{\text{T}}} +
R_{W}^{OS/SS} \cdot N_{W}^{SS, \text{high } m_{\text{T}}} ~\\
\Rightarrow N_{W}^{SS, \text{high } m_{\text{T}}}  &= \frac{N_{\text{data}}^{OS,
\text{high } m_{\text{T}}}  - N_{\text{other}}^{OS, \text{high } m_{\text{T}}}  -
R_{\text{QCD}}^{OS/SS}\cdot(N_{\text{data}}^{SS, \text{high } m_{\text{T}}}  -
N_{\text{other}}^{SS, \text{high } m_{\text{T}}} )}{R_{W}^{OS/SS} -
R_{\text{QCD}}^{OS/SS}} ,
\end{split}
\end{equation}

where $R_{W}^{OS/SS}$ is the ratio between opposite-sign and same-sign \Wjets events
and $R_{QCD}^{OS/SS}$ the ratio between opposite-sign and same-sign QCD events. Using 
equations \ref{eqn:wjets_ss_norm}, the number of \Wjets events in the
opposite-sign, high \mT~region is given by $R_{W}^{OS/SS}\cdot N_{W}^{SS,\text{high} m_{T}}$. 
This is extrapolated to the number of \Wjets events in the signal region at low \mT~ as:

\begin{equation}\label{eqn:wjets_os_norm}
N_{W}^{OS,\text{low} m_{T}} = \frac{N_{W,MC}^{OS,\text{low} m_{T}}}{N_{W,MC}^{OS,\text{high} m_{T}}}\cdot R_{W}^{OS/SS} \cdot N_W^{SS,\text{high }m_{T}},
\end{equation}

which is the estimate of the number of \Wjets events in the opposite-sign, high \mT, region
multiplied by the ratio of the number of \ac{MC} events in the opposite-sign, low \mT~ region to the number of \ac{MC} events in the opposite-sign, high \mT~region. This means that
the \ac{MC} samples are used to derive a high \mT-to-low \mT extrapolation factor.

The use of the method presented relies on knowledge of $R_{W}^{OS/SS}$,
$R_{QCD}^{OS/SS}$, and on these two ratios not being too similar to each other. 
The ratio $R_{QCD}^{OS/SS}$ is measured in an anti--isolated
control region in data; this is described in section ADD REF. $R_{W}^{OS/SS}$ is 
taken from the \Wjets \ac{MC} samples, and is found to be between 4 and 5, while $R_{QCD}^{OS/SS}$
is close to 1.

The method described so far works well in the no b-tag categories, but in the b-tag category
the \ttbar background dominates. For this reason the estimate of the number
of \Wjets events in this category is made with a relaxed category selection where the b-tagging
requirement itself is removed, but the jet requirements still stand. Events with at least one 
jet with \pT$>20$ GeV and with $|\eta|<2.4$, but at most one jet with \pT$>30$ GeV and $|\eta|<4.7$, are therefore selected. The final \Wjets estimate in the b-tag category signal
region is determined by the estimate given by the number of \Wjets events
estimated in the 1-jet selection, multiplied by an extrapolation factor 
$\frac{N_{W,MC}^{OS,\text{low } m_{T},\text{b-tag category}}}{N_{W,MC}^{OS,\text{low }m_{\text{T}},\text{1-jet selection}}}$ ADD FIGURES

\subsubsection{QCD OS/SS ratio}
\label{sec:mssm_bkgs_etmt_qcdosss}
Studies of QCD OS/SS ratio go here

\subsubsection{QCD normalisation}
\label{sec:mssm_bkgs_etmt_qcdnorm}
The QCD normalisation is estimated by inverting the opposite-sign requirement
of the di-tau pair in the signal region. The yield is taken from the same--sign
region with otherwise identical cuts to the opposite--sign region. The contributions
from other backgrounds in this region are subtracted to give an estimate of the number
of QCD events in the same--sign region. For all backgrounds apart from \Wjets the
yields to subtract are estimated using \ac{MC} samples. The number of \Wjets events
expected in this region is given by
\begin{equation}\label{eqn:wjets_qcdsub}
N_{W,SS SR} = \frac{N_{MC,SS SR}}{N_{MC,SS high mT}}N_{W,SS high mT}
\end{equation}

Because opposite--sign and same--sign QCD events do not
necessarily appear in equal amounts the number of QCD
events obtained by subtracting other backgrounds from the
observed number of events in the same--sign region is multiplied
by $R_{QCD}^{OS/SS}$ as derived in section \ref{sec:mssm_bkgs_etmt_qcdosss} 
to obtain an estimate of the number of QCD events in the signal region.

\subsubsection{Control regions in the fit}
\label{sec:mssm_bkgs_etmt_ctrl}
Several control regions in data are used for the estimation
of the QCD and \Wjets backgrounds: the same--sign and 
opposite--sign high \mT~ regions, as well as the same--sign
low \mT~region. This leads to three control regions used 
in each category of both the \mutau and \etau channels to determine
the initial estimate of the background normalisations.
These control regions are included in a simultaneous fit
with the signal regions to obtain the final results.

\subsection{QCD}
\label{sec:mssm_bkgs_qcd}
This section describes the QCD background
estimation in the \tautau and \emu channels.

\subsubsection{\texorpdfstring{\tautau channel}{tau tau channel}}
\label{sec:mssm_bkgs_qcd_tt}
In the \tautau channel the QCD background is by far the 
dominant background. The normalisation and shape 
of this background are estimated from a sideband with loosened 
isolation requirements with respect to the signal region. 
In the no b-tag category the sideband used is determined
by having the tau with highest \pT~ pass the tight working
point of the tau ID discriminator, as in the nominal selection.
The other hadronic tau in the pair does not pass the tight working point,
but does pass the medium working point. This sideband is 
chosen as it is as close to the signal region as possible, and 
this should minimise biases in the shape of the total transverse mass
distribution. Other backgrounds
in this sideband are subtracted from the observation to give
the QCD estimate. Differences in normalisation due to
the use of a loosened sideband are corrected for by loose-to-tight isolation
scale factor. This correction factor is measured as
\begin{equation}\label{eqn:tautau_qcd}
R_{QCD}^{\text{loose}\rightarrow\text{tight}} = \frac{N_{obs}^{SS,\text{nominal isolation}}-N_{\text{other bkgs}}^{SS,\text{loosened isolation}}}{N_{obs}^{SS,\text{loosened isolation}}-N_{\text{other bkgs}}^{SS,\text{loosened isolation}}}.
\end{equation}

So this takes the ratio between the observed data with other
backgrounds subtracted in the region equivalent to the signal region, but with the
charge requirement of the pair inverted, and the region equivalent to the sideband
with loosened isolation but with the charge requirement on the pair inverted.

An analogous method is used for this estimate in the 
b-tag category, however, the sideband as used for the 
no b-tag category does not contain enough events to 
provide a background estimate. Therefore a sideband where
the highest \pT~tau passes the tight working point of the
tau ID discriminator, and the other tau passes the loose working
point of the discriminator, but not the tight working point, is used.
This sideband is slightly further away from the signal region than the
'tight--medium' sideband INSERT FIGURE. The bias from using this looser
sideband has been assessed and has a less than 1$\sigma$ effect.
FIXME THIS ISN'T VERY USEFUL INFO!

\subsubsection{\texorpdfstring{\emu channel}{e mu channel}}
\label{sec:mssm_bkgs_qcd_em}
In the \emu channel the QCD multijet background
is estimated by inverting the charge requirement
of the pair, considering the same--sign region
with otherwise identical cuts to the signal region.
Other backgrounds present in this region are subtracted.
As for the \etau and \mutau channels, the number of
QCD events with opposite--sign \emu pairs is not
necessarily equal to the number of QCD events
with same--sign \emu pairs and therefore the ratio
of opposite--sign to same--sign pairs is measured by inverting
the isolation requirements on the electron or muon. Both
leptons need to satisfy $I_{\text{rel}} < 0.4$ and at 
least one of them needs to fail the nominal isolation requirement.
The opposite--sign to same--sign ratio is parameterised in terms
of lepton kinematics and the separation in $\Delta R$ between the
two leptons. These ratios are then applied to the same--sign region
QCD estimate to give a QCD estimate in the signal region. 
Because the opposite--sign to same--sign ratios are measured
before applying the categorisation, and \ac{MC} studies suggest
that the opposite--sign to same--sign ratio is different in the b-tag
category than in the no b-tag category, an extra scale factor of 
1.45/2.20 is applied to the QCD estimate in this category.

\subsection{\texorpdfstring{\ttbar}{ttbar}}
\label{sec:mssm_bkgs_tt}
The \ttbar shape and normalisation are estimated from \ac{MC} 
samples and are checked against data in a control
region with a \ttbar purity of 91\%. This control region
is defined as $D_{\zeta} < -20$ GeV and \MET $>80$ GeV in 
the \emu channel. INSERT PLOT
In the \mutau, \etau and \tautau channels
the \ttbar contribution is split into
two components, one with real taus and 
one without. The component with real taus is composed
of \ttbar events in which the hadronic tau is matched
to a generator level tau. In the fully hadronic channel
both taus need to be generator matched to a hadronically
decaying tau.

\subsection{Other backgrounds}
\label{sec:mssm_bkgs_other}
For all channels the di--boson plus 
single--top background is small.
Both normalisation and shape are estimated from \ac{MC}
samples. For the \etau, \mutau and \tautau channels
this background contribution is split into a component
where the hadronically decaying tau originates from a real
tau, and one where it does not. This is done in a similar
way as for the \ttbar background
In the \tautau and \emu channels the \Wjets background
is less important than in the \etau and \mutau channels, and both
its shape and normalisation are estimated from the
\ac{MC} samples.

\section{Systematic uncertainties}
\label{sec:mssm_uncs}
Just like for the analysis presented in chapter \ref{chap:hhh}
two types of systematic uncertainty are considered. Normalisation
uncertainties only affect the yield of a process while shape
uncertainties affect both the process normalisation, as well as the shape
of the \mTtot~ distribution. The uncertainties are taken into account 
in the final result as described in section \ref{sec:hhh_results_extraction}.

\subsection{Normalisation uncertainties}
\label{sec:mssm_uncs_norm}
\subsubsection*{Luminosity uncertainty}
The uncertainty on the luminosity measurement amounts to 6.2\% for
data collected during 2016 \cite{cms-pas-lum-15-001}, and it is
applied to all processes for which the normalisation was estimated 
using \ac{MC} samples.
\subsubsection*{Identification, isolation and trigger efficiencies}
\subsubsection*{jet$\rightarrow\Pgt_{h}$ fake rate}
\subsubsection*{$\Pe\rightarrow\Pgt_{h}$ and $\Pgm\rightarrow\Pgt_{h}$ fake rate}
\subsubsection*{Jet energy scale uncertainty}
\subsubsection*{B-tag scale factors}
\subsubsection*{\MET resolution and response}
\subsubsection*{Background normalisation}
\subsubsection*{Theory uncertainties}

\subsection{Shape uncertainties}
\label{sec:mssm_uncs_shape}
\subsubsection*{$\Pgt_{h}$ energy scale}
\subsubsection*{Electron energy scale}
\subsubsection*{High-\pT~ $\Pgt_{h}$ ID efficiency}
\subsubsection*{Top quark \pT~ reweighting}
\subsubsection*{Drell-Yan shape reweighting}
\subsubsection*{Jet$\rightarrow\Pgt_{h}$ fake rate shape reweighting}
